Reproducibility of SNV-calling in multiple sequencing runs from single tumors

### 2015-06-24 PAPER/paper.tex
moved the keynote doucument with figure 1 to FIGURE_SCRIPTS

\documentclass[11pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
\usepackage[T1]{fontenc}
\usepackage{authblk}

@@

%%% Title and author are here
\title{Reproducibility of SNV-calling in multiple sequencing runs from single tumors}
\author[1]{Dakota Z. Derryberry\thanks{dakotaz@utexas.edu}}
\author[2,3]{Matthew C. Cowperthwaite}
\author[1,4]{Claus O. Wilke} 
\affil[1]{The University of Texas at Austin, Cell \& Molecular Biology}
\affil[2]{St. David's NeuroTexas Institute Research Foundation}
\affil[3]{Center for Systems and Synthetic Biology, The University of Texas at Austin}
\affil[4]{The University of Texas at Austin, Integrative Biology}

@@

>>>>

\documentclass[11 pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
\usepackage[T1]{fontenc}
\usepackage{authblk}

@@

%%% Title and author are here
\title{Reproducibility of SNV-calling in multiple sequencing runs from single tumors}
\author[1]{Dakota Z. Derryberry\thanks{Dakota Z. Derryberry: 2500 Speedway, Austin, TX, 78712; (512)232-2459; dakotaz@utexas.edu}}
\author[2,3]{Matthew C. Cowperthwaite}
\author[1,4]{Claus O. Wilke} 
\affil[1]{Cell \& Molecular Biology, The University of Texas at Austin, Austin, TX USA}
\affil[2]{St. David's NeuroTexas Institute Research Foundation, Austin, TX, USA}
\affil[3]{Center for Systems and Synthetic Biology, The University of Texas at Austin, Austin TX, USA}
\affil[4]{Integrative Biology, The University of Texas at Austin, Austin, TX, USA}

@@

\clearpage
